---
title: "R Notebook"
output: html_notebook
---

## WLA Program Summary


```{r}
library("tidyverse")
wla <- read_csv("data/wla.csv")
wla
```

Only 11 states have started disbursing funds. 

```{r}
wla %>% filter(`Program Start` == "Started")
```
Among States that have not disbursed funds yet, 12 will do so in september, 2 in October, and 25 have not yet announced when their programs start. 
```{r}
wla %>% filter(str_detect(`Program Start`, 'September'))
```

```{r}
wla %>% filter(str_detect(`Program Start`, 'October'))
```

```{r}
wla %>% filter(is.na(`Program Start`)) 
```
Only 5 states will provide the extra $100

```{r}
wla %>% filter(`Enhanced Benefit Amount` == "$400")
```
Based on the fact that 11 states started their programs in early September and 12 more will do so at some point this month, I say we should assign 10% of the funds to Q3 (calendar year) and 90% to Q4 (calendar year). So `r 44*0.1` in Q3 and `r 44*0.9` in Q4. At an annualized rate this is `r 44*0.1*4` in Q3 and `r 44*0.9*4` in Q4. 
