------------------------------------------------------------------------

---
title: 'American Rescue Plan'

author: ' Manuel Alcala Kovalski and Sophia Campbell'
date: "`r Sys.Date()`"
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
output:
  html_document:
    toc: true # table of content true
    toc_float: true
    toc_depth: 2
    number_sections: false 
    theme: united
    highlight: zenburn 
    fig.retina: 2 
    fig_width: 4
    fig_heigth: 6
    self_contained: yes
    css: [style.css]
    background: #FAFAFA
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  results = 'asis',
  tidy.opts=list(width.cutoff=60),
  tidy=TRUE, 
  echo = FALSE,

  
  #cache = TRUE,
  fig.align = "center",
  fig.show = "hold",
  fig.width=8, 
  fig.asp=0.9,
  out.width = "1000px",
  fig.path = "results/3-2021/figures-arp/",
  fig.retina = 2,
  fig.showtext = TRUE,
  fig.pos = "t",
  dpi = if (knitr::is_latex_output()) 72 else 300,
  dev.args = list(png = list(type = "cairo-png")), 
  optipng = "-o1 -quiet"
)
  
)
library(knitr)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::knit_hooks$set(optipng = hook_optipng)
knitr::knit_hooks$set(pngquant = hook_pngquant)
```

```{r libs}
library(targets)
library(tarchetypes)
source('R/packages.R')
source('R/functions.R')
library('conflicted')
conflict_prefer('filter', 'dplyr')
conflict_prefer("month", "lubridate")
conflict_prefer('year', 'lubridate')
conflict_prefer('lag', 'dplyr')

current_month <- glue::glue(lubridate::month(lubridate::today()), '-', lubridate::year(lubridate::today()))
components <- get_components_names()

library('targets')
library('tidyverse')
library('magrittr')
library('ggthemes')
library('ggtext')
library('ggthemes')
library('gridExtra')
library('fim')
library('lubridate')
library('glue')
library('readxl')
library('tsibble')
library('gghutchins')
library('showtext')

conflicted::conflict_prefer('filter', 'dplyr')
conflicted::conflict_prefer('geom_col', 'ggplot2')
conflicted::conflict_prefer('geom_line', 'ggplot2')


last_month <- get_previous_month()
current_month <- get_current_month()
tar_load(last_hist_date)
tar_load(last_proj_date)
tar_load(fim)
theme_set(theme_hutchins())
```


```{r, include = FALSE}
arp_spending <-
  fim %>% 
   mpc_arp_non_health_grants() %>% 
      summarize(date, non_health_grants_post_mpc,
                across(.cols = all_of(c('federal_ui_arp', 'state_ui_arp', 'other_vulnerable')),
                    .fns = ~ mpc_vulnerable_arp(.x),
                    .names = '{.col}_post_mpc'),
             across(.cols = all_of(c('rebate_checks_arp', 'other_direct_aid')),
                    .fns = ~ mpc_direct_aid_arp(.),
                    .names = '{.col}_post_mpc'),
             health_grants_arp_post_mpc = mpc_health_outlays(health_grants_arp),
             aid_to_small_businesses_post_mpc = mpc_small_businesses_arp((aid_to_small_businesses)) 
      ) %>% 
  rename_with(~ gsub('_post_mpc', '', .x)) %>% 
    filter(date > '2020-12-31' & date < '2025-03-30')

arp_cont <-
  fim %>% 
   filter(date > '2020-12-31' & date < '2024-12-31') %>% 
   select(date, federal_ui_arp_cont, rebate_checks_arp_cont, other_direct_aid_cont, other_vulnerable_cont, aid_to_small_businesses_cont, non_health_grants_cont, health_grants_arp_cont,
          federal_cont, federal_cont_no_arp, fiscal_impact)
```


```{r arpa-final}
arp_cont %>% 
  summarise(date, 
            arp_cont =  health_grants_arp_cont + non_health_grants_cont +
            federal_ui_arp_cont + rebate_checks_arp_cont + other_direct_aid_cont + other_vulnerable_cont + aid_to_small_businesses_cont ) %>% 
  pivot_longer(-date) %>% 
  mutate(date =  yearquarter(date)) %>% 
  ggplot(aes(x = date, y = value, fill = name)) +
  geom_col() +
  scale_fill_hutchins() +
    theme(axis.title.y = element_text(angle = 90, vjust = 0.5, hjust=0.5),
          legend.position = 'none') +
  scale_y_continuous(name = "Percentage points", 
                     labels = scales::label_percent(scale = 1, accuracy = 1),
                     breaks = seq(-2, 6, 1)) +
       scale_x_yearquarter(breaks = waiver(),
                          date_breaks = '3 months',
                          date_labels = "Q%q") +
      facet_grid( ~ year(date),
                  space = "free_x",
                  scales = "free_x",
                  switch = "x")  +
geom_hline(yintercept = 0, size = 0.4, linetype = 2, alpha =  1, color = 'black') +
  labs(title = 'Contribution of the American Rescue Plan to real GDP growth', 
       caption =  '**Source**: Hutchins Center calculations from Bureau of Economic Analysis and Congressional Budget Office data') +
  theme(plot.background = element_rect(fill = '#FAFAFA', colour = '#FAFAFA'))
```
```{r arp-commponents-stacked}
arp_cont %>% 
  select(date, 
            health_grants_arp_cont , non_health_grants_cont ,
            federal_ui_arp_cont , rebate_checks_arp_cont , other_direct_aid_cont, other_vulnerable_cont, aid_to_small_businesses_cont ) %>% 
  mutate(date =  yearquarter(date)) %>% 
  pivot_longer(-date) %>% 
  filter(date <= yearquarter('2026 Q1')) %>% 
  ggplot(aes(x = date, y = value, fill = name)) +
  geom_col(width = 30) +
  scale_fill_hutchins(labels = c('Aid to small businesses','Unemployment insurance',  'Medicaid expansion', 'Federal purchases^1', 'Other direct aid^2', 'Other aid to vulnerable households^3', 'Rebate Checks' ), pal = 'categorical', rev = TRUE) +
    theme(legend.position = 'top',
        legend.direction  = 'horizontal',
        legend.justification = 'left') +
  scale_y_continuous(name = 'Percentage points', labels = scales::label_percent(scale = 1, accuracy  =  1),
                     breaks = seq(-3, 6, 1)) +

  guides(fill=guide_legend(ncol = 2)) +
      scale_x_yearquarter(breaks = waiver(),
                          date_breaks = '3 months',
                          date_labels = "Q%q") +
      facet_grid( ~ year(date),
                  space = "free_x",
                  scales = "free_x",
                  switch = "x")  +
geom_hline(yintercept = 0, size = 0.35, linetype = 2, alpha =  0.8) +
  theme(axis.title.y = element_text(angle = 90, vjust = 0.5, hjust=0.5)) +
  labs(
    ylab = 'Percentage points',
    title = 'Components of the contribution of the American Rescue Plan Act to real GDP growth', 
       caption = '<br>**Source:** Hutchins Center calculations from Bureau of Economic Analysis and Congressional Budget Office data.<br><br>
    ^1 Federal purchases include direct federal spending related to COVID-19 containment and vaccination as well as state and local purchases financed by federal grants;<br>
       ^2 Other direct aid includes the Child Tax Credit, the Earned Income Tax Credit, child care for workers, and dependent care for families; <br>
       ^3 Other aid to vulnerable households includes food, housing and emergency assistance, ratepayer protection, assistance for older Americans, premium tax credits, and subsidies for COBRA premiums.
') +
   theme(plot.background = element_rect(fill = '#FAFAFA', colour = '#FAFAFA'))

knitr::include_graphics(file.path(here::here(),"images","HC_NEW_BROOKINGS_RGB.jpg"))
```

