---
title: "NIPA Consistent FIM Check"
author: "Manuel Alcalá Kovalski"
date: "12/2/2020"
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
vignette: |
  %\VignetteIndexEntry{The comparedf function for NIPA}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r include = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, results = 'asis', comment='', warning = FALSE)
options(width = 120)
```

```{r}
source('src/packages.R')
```

# Contributions to Percent Change in Real Gross Domestic Product (NIPA)
First, we want to load Table 1.1.2. "Contributions to Percent Change in Real Gross Domestic Product" from [BEA](https://apps.bea.gov/iTable/iTable.cfm?reqid=19&step=3&isuri=1&nipa_table_list=2&categories=survey) for quarterly data between 2018 and 2020. 
```{r}
drake::loadd(fim_nipa_consistent)
library(bea.R)
beaKey <- '6937C372-8AEE-4BFD-B991-1A469B942C41'

beaSpecs <- list(
	'UserID' = beaKey ,
	'Method' = 'GetData',
	'datasetname' = 'NIPA',
	'TableName' = 'T10102',
	'Frequency' = 'Q',
	'Year' = '2018, 2019, 2020'
)

nipa_contributions <-
  beaGet(beaSpecs,  asTable = TRUE, asWide = FALSE) %>%
  as_tibble()
library(kableExtra)
paged_table(nipa_contributions, options(row.print = 11))
```
In order to compare our methodology to the BEA's, we need to look at "Government consumption expenditures and gross investment" (Line item 22) and its subcomponents: Federal (Line item 23) and State and local (Line item 26). 

```{r nipa-condensed}
nipa_contributions <-
  nipa_contributions %>%
  select(TimePeriod, LineDescription, DataValue) %>%
  filter(LineDescription %in% c('Government consumption expenditures and gross investment', 'Federal', 'State and local')
  ) %>%  
  mutate(TimePeriod = as.yearqtr(TimePeriod)) %>%
  rename(date = TimePeriod) %>%
  pivot_wider(names_from = LineDescription, values_from = DataValue)

paged_table(nipa_contributions, options(rows.print = 11, max.print = 11))
```


```{r, include = FALSE}

fim_nipa_consistent
```


```{r}

fim_nipa_contributions <-
  fim_nipa_consistent %>%
  mutate(date = as.yearqtr(date)) %>%
  rename(federal_purchases_cont = federal_cont,
         state_local_purchases_cont = state_local_cont) %>%
  select(date, fiscal_impact, federal_purchases_cont, state_local_purchases_cont) %>%
  filter(date >= '2018 Q1' & date <= '2020 Q3') 
  

```

```{r}
paged_table(fim_nipa_contributions, options(digits = 2))
```

```{r, results = 'asis', include = FALSE}
library('arsenal')
```

# Comparison 
Differences between the NIPA consistent FIM and the BEA data are tolerated up to 0.06 due to potential rounding errors.

The differences deteced table (all the way at the bottom) in the summary below shows that our estimates match the BEA's except for 2020 Q2 and 2020 Q3.

In particular, our estimates for the contribution of Federal and State & Local purchases for 2020 Q2 are both 0.2 lower than BEA. Similarily, our 2020 Q3 estimate is 0.11 lower for both Federal and State. 
```{r, results = 'markup'}


contributions_comparison <-
  comparedf(fim_nipa_contributions , 
            nipa_contributions,
            tol.vars = c(fiscal_impact = 'Government consumption expenditures and gross investment',
                             federal_purchases_cont = "Federal",
                             state_local_purchases_cont = "State and local"),
            tol.num.val = 0.01
) 

```

```{r}
summary(contributions_comparison)

```
```{r}
wide <- fim_nipa_contributions %>% left_join(nipa_contributions, by = 'date') %>% pivot_longer(where(is.numeric)) %>% arrange(name) %>% pivot_wider(names_from = date)

paged_table(wide)
```


